Semantic browsing of sound databases \\ without keywords

### 2016-07-05 final/lafaySsf2016.tex
creating final version
photos

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/music_mds.png} 
\end{center}
\caption{\label{figXP3music} Acoustical Display for the instrument sound dataset (AD). Colors and legend are removed during the experiment.}
\end{figure}

@@

\biography{\textbf{Gr\'egoire Lafay}}{gfx/lafay.jpg}{IRCCYN, Ecole Centrale de Nantes, France}

\biography{\textbf{Nicolas Misdariis}}{gfx/lafay.jpg}{IRCAM, France}

\biography{\textbf{Mathieu Lagrange}}{gfx/lagrange.jpg}{IRCCYN, Ecole Centrale de Nantes, France}

\biography{\textbf{Mathias Rossignol}}{gfx/rossignol.jpg}{STMS Ircam-CNRS-UPMC, France}

>>>>

\graphicspath{{../}}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{gfx/music_mds_bw.png} 
\end{center}
\caption{\label{figXP3music} Acoustical Display for the instrument sound dataset (AD). Colors and legend are removed during the experiment.}
\end{figure}

@@

\biography{\textbf{Gr\'egoire Lafay}}{../gfx/lafay.jpg}{IRCCYN, Ecole Centrale de Nantes, France}

\biography{\textbf{Nicolas Misdariis}}{../gfx/misdariisBw.jpg}{STMS Ircam-CNRS-UPMC, France}

\biography{\textbf{Mathieu Lagrange}}{../gfx/lagrange.jpg}{IRCCYN, Ecole Centrale de Nantes, France}

\biography{\textbf{Mathias Rossignol}}{../gfx/rossignol.jpg}{STMS Ircam-CNRS-UPMC, France}
